
```{r getData, eval=FALSE}
# clean memory
rm(list = ls()) 
# link
link='https://github.com/EvansDataScience/data/raw/master/eduwa.rda'

#getting the data TABLE from the file in the cloud:
load(file=url(link))
```

As we have many values, it is difficult to share a clear insight. However, we could try a different idea:

```{r, eval=FALSE}
# sum of reduced lunches given per county
CountyCount_LR=aggregate(data=eduwa,
                         Reduced.Lunch~County,
                         FUN=sum)
#see
CountyCount_LR
```

Now you have much less cases, just 39. Let's order by count in decreasing order:

```{r, eval=FALSE}
# order and minus (-) for decreasing
CountyCount_LR=CountyCount_LR[order(-CountyCount_LR$Reduced.Lunch),]
head(CountyCount_LR,10)
```

Let's add the percent, and cummulative percent and cummulative count:

```{r, eval=FALSE}
CountyCount_LR$Percent=CountyCount_LR$Reduced.Lunch/sum(CountyCount_LR$Reduced.Lunch)
CountyCount_LR$PercentCum=cumsum(CountyCount_LR$Percent)
CountyCount_LR$Reduced.Lunch.Cum=cumsum(CountyCount_LR$Reduced.Lunch)
# see some:
head(CountyCount_LR,20)
```



Let's plot the cumulative count as a barplot:

```{r, eval=FALSE}

base2=ggplot(data=CountyCount_LR,
             aes(x=County,Reduced.Lunch.Cum)) + theme_classic()
base3=base2+scale_x_discrete()
bar2=base3  +geom_bar(stat = "identity")
bar2=bar2 + coord_flip() 
bar2
```

The previous plot is NOT informative, this is better:

```{r, eval=FALSE}
# altering previous base3
base3=base2+scale_x_discrete(limits=CountyCount_LR$County)
bar2=base3  +geom_bar(stat = "identity")
bar2=bar2 + coord_flip() 
bar2

```

We could redo **bar2** by using the other columns to show the Pareto principle:
```{r, eval=FALSE}
bar2=base3  +geom_bar(stat = "identity",color='grey90',
                      aes(fill=PercentCum<0.8),
                      show.legend = F)
bar2=bar2 + coord_flip()

bar2
```

Above, we just altered the _border_ of the bars (color); and we told ggplot to fill the bars _conditionally_. The default fill color was chosen. If you want to customize the fill color, do this:

```{r, eval=FALSE}
# I only need one fill color, that is why I put 'NA":
bar2=bar2 +scale_fill_manual(values=c(NA,"grey90"))
bar2
```

The last version tries to highlight some counties. This last step could help more:

```{r, eval=FALSE}
# this is a condition outside ggplot.
# it says what counties add to 80%
counties80=CountyCount_LR[CountyCount_LR$PercentCum<0.8,"County"]

# now we use that here, to alter the face of text:
bar2=bar2 + theme(axis.text.y = element_text(face=ifelse(CountyCount_LR$County%in%counties80,"bold","plain"),size=9))
bar2
```

The last plot shows the counties that altogether sum the 80% of reduced lunches offer in the state of Washington. Of course, there is a propeo pareto plot for this cases:

```{r, eval=FALSE}
library(ggQC) # install this previously

base4=ggplot(data=CountyCount_LR,
             aes(x=County,y=Reduced.Lunch)) + theme_classic()
pare1=base4 + stat_pareto() 
pare1

```

That was fast. However, some extra work might be needed:

```{r, eval=FALSE}
# computing intercepts
interX=length(counties80)
interY=max(CountyCount_LR$Reduced.Lunch.Cum)*0.8

# annotating intercepts
pare2=pare1 + geom_vline(xintercept = interX,
                         linetype="dashed", color='grey90') 
pare2=pare2 + geom_hline(yintercept =interY,
                         linetype="dashed", color='grey90') 
pare2 + theme(axis.text.x = element_text(angle = 30, hjust = 1,face=ifelse(CountyCount_LR$County%in%counties80,"bold","plain")))
```


All these plots give us an idea of **distribution**: how lunches are distributed among counties. 